An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/trans.tex
config: main balance and trans

\begin{table}
\caption{Table of types, along with associated templates, used in \app}
  \begin{tabular}{| l |  l |}
    \hline
    Type &  Template \\ \hline
    Integer & $X = Y, X\neq Y, X \leq Y, X < Y, X * Y < Z, \ldots $\\ \hline
    String & $\textsf{substr}(U, V), \textsf{prefix}(U,V), \textsf{suffix}(U,V), \ldots$   \\ \hline
    File Path & $\textsf{isFile}(F), \textsf{isDir}(D),\ldots$   \\ \hline
    Size & Similar to integers   \\ \hline
    Port & $P_1 > P_2$ \\ \hline
    IP Addr.  & $\textsf{sameSubnet}(addr1, addr2)$   \\

>>>>

\begin{table}
\caption{Table of types, along with associated templates, used in \app}
  \begin{tabular}{| l |  l |}
    \hline
    Type &  Template \\ \hline
    \hline
    Integer & $X = Y, X\neq Y, X \leq Y, X < Y, X * Y < Z, \ldots $\\ \hline
    String & $\textsf{substr}(U, V), \textsf{prefix}(U,V), \textsf{suffix}(U,V), \ldots$   \\ \hline
    File Path & $\textsf{isFile}(F), \textsf{isDir}(D),\ldots$   \\ \hline
    Size & Similar to integers   \\ \hline
    Port & $P_1 > P_2$ \\ \hline
    IP Addr.  & $\textsf{sameSubnet}(addr1, addr2)$   \\
